Aligning marine species range data to better serve science and conservation

### 2016-02-25 ms_2_intro_res_disc.Rmd
meh

>>>>

Conclusions:
combine datasets for increased number of species; identify data-poor species to improve confidence in range estimates
differences in methodology create significant differences in results; errors of both commission and omission
importance to conservation management - different types of errors have different implications
